R Notebook

### 2018-03-12 paper/docs/04_Modelresults_50.Rmd
its getting better...

# 2. Model Results

@@

## Label topics

@@

```{r eval=FALSE, fig.height=12, fig.width=5}
topic <- 50

plotQuote(c(paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n"),
            paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n"),
            paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n"),
            paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n"),
            paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n"),
            paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n"),
            paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n")))
```

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "B90/ Die Grüne", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "Merkel vs. Schulz", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Decision about GroKo in the SPD", 18, "Election in Niedersachsen", 19, "N.Lammert", 20, "AfD", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder vs. Seehover, refugee cap", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Reelections after Jamaica failure", 27, "Jamaica caolition talks", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "F.Petri, AfD", 31, "D.Trump, Russia", 32, "Gauland, Weidel, AfD", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU, Spahn", 47, "Church", 48, "public budget statistics, Education and Healthcare", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)

@@

## Posterior distribution (gamma)

@@

The probability of each topic for documents 1-5 can be plotted as:

```{r}
theta %>%
  filter(document < 6) %>%
  ggplot(aes(factor(topic), gamma, 
             fill = factor(document))) +
  geom_col(position = "dodge") +
  scale_fill_manual(values = col,
                    guide = guide_legend(
                      nrow = 1
                    )) +
  labs(x = "Topic", fill = "Document",
       title = "Gamma distribution of documents 1-5") +
  theme(legend.position = "bottom") 
```

As you can see, only document 2 cannot be assigned to any topic with a high probability. In the case of the other documents, it is highly likely that it belongs to a particular topic.

@@

## 3.1. Topic proportions

@@

```{r fig.height=8, fig.width=6}
p1 <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
    geom_col(fill=col[1], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10))

@@

Keep only those articles, that are clear & interessting to analyse.

```{r}
keep <- c(1,2,4,10,13,17,20,22,26,27,37,46)
```

## 3.2. Difference in topic prevalence

@@

## Sentiment analysis

@@

#### 1. Load sentiment dictionary.

@@

```{r}
sent <- c(
  # positive Wörter
  readLines("dict/SentiWS_v1.8c_Negative.txt",
            encoding = "UTF-8"),
  # negative Wörter
  readLines("dict/SentiWS_v1.8c_Positive.txt",
            encoding = "UTF-8")
) %>% lapply(function(x) {
  # Extrahieren der einzelnen Spalten
  res <- strsplit(x, "\t", fixed = TRUE)[[1]]
  return(data.frame(words = res[1], value = res[2],
                    stringsAsFactors = FALSE))
}) %>%
  bind_rows %>% 
  mutate(word = gsub("\\|.*", "", words) %>% tolower,
         value = as.numeric(value)) %>%
  # manche Wörter kommen doppelt vor, hier nehmen wir den mittleren Wert
  group_by(word) %>% summarise(value = mean(value)) %>% ungroup

# sent %>% 
#   dplyr::top_n(10, desc(value)) %>%
#   htmlTable::htmlTable()
```

#### 2. Apply the dictionary on the artciles.

We now take each word in each article and assign a sentiment value for that word. I only use articles that have been assigned a topic with a probability of over 90% (gamma > 0.9).

```{r, message=FALSE, warning=FALSE, include=FALSE}
df <- btw.2 %>%
  filter(gamma >= 0.85) %>%
  filter(topic %in% keep)

@@

##### Check the analysis for a set of example documents.

@@

#### 3. Calculate sentiment value by document

We apply two different measurements:

  1. **Weighted** calculates the score based on the weighted values for a word. As explained above, the dictionary places the words on an interval of -1 and 1. The score is then calculated from the sum of the words in a document (which can be assigned to a word from the dictionary) divided by the total number of words in that document.

@@

  2. **Count** calculates the score as the difference of positive and negative words (dummy) divided divided by the total number of words in that document. This value therefore only reflects the relation between positive and negative words, without considering the weighting of these words.

$$
\text{Count}_d = \frac{\text{Sum of positive Words}_d - \text{Sum of negative Words}_d}{\text{Total Words}_d}
$$

@@

  # combine with dataframe
  left_join(., df, 
            by = "document") %>%
  # calculate sentiment
  mutate(sentiment_d = sent_diff_d / text_length,
         sentiment = sent_diff / text_length)
```

#### 4. Plot Sentiment

##### 4.1. by topic
```{r fig.height=4, fig.width=7}
p <- sentDF.values %>%
  group_by(topic_name) %>%
  summarise(sentiment_d = mean(sentiment_d, na.rm=T),
            sentiment = mean(sentiment, na.rm=T),
            obs = n())

## weighted ##
p1 <- ggplot(p, aes(reorder(topic_name, sentiment), 
              sentiment,
              label = obs)) +
  geom_col(fill = col[1], alpha = 0.7) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Weighted") +
  theme(axis.text.y = element_text(size = 8))

## unweighted ##
p2 <- ggplot(p, aes(reorder(topic_name, sentiment), 
              sentiment_d,
              label = obs)) +
  geom_col(fill = col[4], alpha = 0.7) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Count") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

p1 + p2
```

##### 4.2. by site

```{r fig.height=4, fig.width=7}
p <- sentDF.values %>%
  group_by(site) %>%
  summarise(sentiment_d = mean(sentiment_d, na.rm=T),
            sentiment = mean(sentiment, na.rm=T),
            obs = n())

## weighted ##
p1 <- ggplot(p, aes(reorder(site, sentiment), 
              sentiment,
              label = obs)) +
  geom_col(fill = col[1], alpha = 0.7) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Weighted") +
  theme(axis.text.y = element_text(size = 8))

## unweighted ##
p2 <- ggplot(p, aes(reorder(site, sentiment), 
              sentiment_d,
              label = obs)) +
  geom_col(fill = col[4], alpha = 0.7) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  labs(x="", y="",
       title = "Count") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

p1 + p2
```

##### 4.3. By site and topic

```{r fig.height=8, fig.width=12}
p <- sentDF.values %>%
  group_by(site, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            sentiment_d = mean(sentiment_d, na.rm=T),
            obs = n())

p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment, label = obs)) +
  geom_col(fill=col[1], alpha = 0.7) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="",
       title = "Weighted") +
  theme(axis.text.y = element_text(size=8))

p2 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment_d, label = obs)) +
  geom_col(fill=col[4], alpha = 0.7) +
  #geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="",
       title = "Count") +
  theme(axis.text.y = element_text(size=8))

p1 + p2 + plot_layout(ncol = 1)
```

##### 4.4. Radar plot

@@

```{r}
sentDF.values %>%
  group_by(site, topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T)) %>%
  spread(key=topic_name, value=sentiment) -> radar

radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0, legend.position = "right") +
  labs(title = "Weighted")
```

```{r eval=FALSE, include=FALSE}
for (i in stmOut$settings$covariates$yvarlevels) {

  p <-radar %>%
    filter(site == i) %>%
    ggRadar(rescale = F,
            alpha = 0, legend.position = "right") +
    labs(title = i)

  ggsave(p, filename = paste0("../figs/radarchartWeighted_",i,k,".png"), 
         device = "png", dpi = 600)

@@

```{r}
sentDF.values %>%
  group_by(site, topic_name) %>%
  summarise(sentiment = mean(sentiment_d, na.rm=T)) %>%
  spread(key=topic_name, value=sentiment) -> radar

radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0, legend.position = "right") +
  labs(title = "Count")
```

```{r eval=FALSE, include=FALSE}
for (i in stmOut$settings$covariates$yvarlevels) {

  p <-radar %>%
    filter(site == i) %>%
    ggRadar(rescale = F,
            alpha = 0, legend.position = "right") +
    labs(title = i)

  ggsave(p, filename = paste0("../figs/radarchart_",i,k,".png"), 
         device = "png", dpi = 600)

###### Weighted

<img src="../figs/radarchartWeighted_Bild.de35.png", width = "49%">
<img src="../figs/radarchartWeighted_DIE WELT35.png", width = "49%">
<img src="../figs/radarchartWeighted_FOCUS ONLINE35.png", width = "49%">
<img src="../figs/radarchartWeighted_SPIEGEL ONLINE35.png", width = "49%">
<img src="../figs/radarchartWeighted_stern.de35.png", width = "49%">
<img src="../figs/radarchartWeighted_Tagesschau.de35.png", width = "49%">
<img src="../figs/radarchartWeighted_ZEIT ONLINE35.png", width = "49%">

###### Count

<img src="../figs/radarchart_Bild.de35.png", width = "49%">
<img src="../figs/radarchart_DIE WELT35.png", width = "49%">
<img src="../figs/radarchart_FOCUS ONLINE35.png", width = "49%">
<img src="../figs/radarchart_SPIEGEL ONLINE35.png", width = "49%">
<img src="../figs/radarchart_stern.de35.png", width = "49%">
<img src="../figs/radarchart_Tagesschau.de35.png", width = "49%">
<img src="../figs/radarchart_ZEIT ONLINE35.png", width = "49%">

### 5. SenitmantR

```{r}
pacman::p_load(sentimentr)
```

```{r}
sent %>%
  mutate(polarity = value) %>%
  as_key() -> sentiment_df
```

#### Output

We may wish to see the output from sentiment_by line by line with positive/negative sentences highlighted. The highlight function wraps a sentiment_by output to produces a highlighted HTML file (positive = green; negative = pink). Here we look at a random article for each site.

```{r}
df %>% 
  mutate(text_split = get_sentences(text)) %$%
  sentiment(text_split,
               polarity_dt = sentiment_df) -> df_sent

df %>% 
  group_by(site) %>%
  sample_n(1) %>%
  mutate(text_split = get_sentences(title_text)) %$%
  sentiment_by(text_split, site,
               polarity_dt = sentiment_df) %>%
  sentimentr::highlight()
```

[Polarity](polarity.html)

>>>>

# Model Results

@@

## 1. Topic

### 1.1. Label topics

@@

```{r eval=FALSE, fig.height=8, fig.width=4}
topic <- 1

plotQuote(c(paste(sagelabs$covnames[1],":", 
                  paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[2],":",
                  paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[3],":", 
                  paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[4],":", 
                  paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[5],":", 
                  paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[6],":",
                  paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[7],":",
                  paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n"))),
          text.cex = 0.8, width = 40,
          main = paste(topics.df$topic_name[topics.df$topic==topic])
          )
```

```{r}
topics <- matrix(c(1, "SPD", 2, "B90/ Die Grüne & DIE LINKE", 3, "Mix: Akhanli, Guttenberg, Bayern", 4, "Great Coalition debates", 5, "Diesel scandal", 6, "H.Kohl", 7, "Federal Election results", 8, "Europa, Macron, Schäuble", 9, "Mix: political trends, twitter", 10, "Merkel vs. Schulz", 11, "politics & democracy in GER", 12, "Deportation of criminal Refugees", 13, "A.Merkel", 14, "Text processing fail", 15, "Israel, antisemitism, D.Trump", 16, "Mix: political talkshows, Refugees", 17, "Intra-party vote (SPD) about the coalition w CDU/CSU", 18, "Election in Niedersachsen", 19, "R.Lammert", 20, "AfD, Right-wing extremist tendencies", 21, "German armed forces, v.d.Leyen", 22, "SPD, stuffing debates", 23, "CSU, Söder vs. Seehover, refugee cap", 24, "Bundespräsident F.-W.Steinmeier", 25, "Election polls", 26, "Reelections vs. Great Coalition after Jamaica failure", 27, "Jamaica caolition talks", 28, "G20 in Hamburg", 29, "Federal Constitutional Court, Ministry of the Interior", 30, "F.Petri, AfD", 31, "D.Trump, Russia", 32, "Gauland, Weidel, AfD", 33, "German armed forces, Mali", 34, "Mix: Children, Education, Women", 35, "Left- rightwing Terror, police reports", 36, "Mix: people, Germany, democracy", 37, "AfD in parliament", 38, "EU policies", 39, "Mix: Terror attacks", 40, "Mix: Metoo, SPD", 41, "Terror attack Berlin (Amri)", 42, "Refugee family reunion", 43, "Mix: studies", 44, "Federal Constitutional Court (NSU, Franco, Terror)", 45, "Mix: minister of the interior, environment", 46, "CDU, Spahn", 47, "Church", 48, "public (budget) statistics, Education/ Healthcare/ Digital policies", 49, "Turkey", 50, "Höcke, Holocaust"), ncol=2, byrow=T)

@@

### 1.2. Posterior distribution (gamma)

@@

@@

### 1.3 Topic proportions

@@

```{r fig.height=8, fig.width=8}
p1 <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
    geom_col(fill=col[1], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10))

@@

```{r eval=FALSE, include=FALSE}
btw.2 %>% filter(topic == 46) %>%
  filter(!grepl("Geißler", title)) %>%
  select(title, url, site) %>%
  htmlTable::htmlTable(align = "l")
```

We will conduct our further analysis on 15 selected topics which relate to political parties.

```{r}
keep <- c(1,2,4,10,13,17,20,22,23,26,27,30,32,37,46)
```

### 1.4. Difference in topic prevalence

@@

## 2. Tone

### 2.1. Plotquote

The plotQuote function allows to inspect die most common words of a topic for each covariate.

```{r eval=FALSE, fig.height=8, fig.width=4}
for (topic in keep) {

  png(filename = paste0("../figs/plotquote",topic,".png"), width = 300,
      height = 700)

  plotQuote(c(paste(sagelabs$covnames[1],":", 
                  paste(sagelabs$cov.betas[[1]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[2],":",
                  paste(sagelabs$cov.betas[[2]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[3],":", 
                  paste(sagelabs$cov.betas[[3]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[4],":", 
                  paste(sagelabs$cov.betas[[4]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[5],":", 
                  paste(sagelabs$cov.betas[[5]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[6],":",
                  paste(sagelabs$cov.betas[[6]]$problabels[topic,], collapse="\n")),
            paste(sagelabs$covnames[7],":",
                  paste(sagelabs$cov.betas[[7]]$problabels[topic,], collapse="\n"))),
          text.cex = 0.8, width = 40,
          main = paste(topics.df$topic_name[topics.df$topic==topic])
          )
  dev.off()
}
```

<img src="../figs/plotquote1.png", width = "30%">
<img src="../figs/plotquote2.png", width = "30%">
<img src="../figs/plotquote4.png", width = "30%">
<img src="../figs/plotquote10.png", width = "30%">
<img src="../figs/plotquote13.png", width = "30%">
<img src="../figs/plotquote17.png", width = "30%">
<img src="../figs/plotquote20.png", width = "30%">
<img src="../figs/plotquote22.png", width = "30%">
<img src="../figs/plotquote23.png", width = "30%">
<img src="../figs/plotquote26.png", width = "30%">
<img src="../figs/plotquote27.png", width = "30%">
<img src="../figs/plotquote30.png", width = "30%">
<img src="../figs/plotquote32.png", width = "30%">
<img src="../figs/plotquote37.png", width = "30%">
<img src="../figs/plotquote46.png", width = "30%">

### 2.2. Sentiment analysis

@@

#### 2.2.1. Load sentiment dictionary.

@@

```{r}
sent <- c(
  # positive Wörter
  readLines("dict/SentiWS_v1.8c_Negative.txt",
            encoding = "UTF-8"),
  # negative Wörter
  readLines("dict/SentiWS_v1.8c_Positive.txt",
            encoding = "UTF-8")
) %>% lapply(function(x) {
  # Extrahieren der einzelnen Spalten
  res <- strsplit(x, "\t", fixed = TRUE)[[1]]
  return(data.frame(words = res[1], value = res[2],
                    stringsAsFactors = FALSE))
}) %>%
  bind_rows %>% 
  mutate(word = gsub("\\|.*", "", words) %>% tolower,
         value = as.numeric(value)) %>%
  # manche Wörter kommen doppelt vor, hier nehmen wir den mittleren Wert
  group_by(word) %>% summarise(value = mean(value)) %>% ungroup
```

#### 2.2.2. Apply the dictionary on the artciles.

To carry out the sentiment analysis we filter some documents from the corpus:

  1. Articles that have been assigned a topic with a probability of over 75% (gamma > 0.75).
  2. Articles assigned to one of the above mentioned topics.
  3. Some manual cleanups

After applying these filters, we still have about 2500 articles left to conduct the sentiment analysis. We now take each word in each article and assign a sentiment value for that word.

```{r, message=FALSE, warning=FALSE, include=FALSE}
df <- btw.2 %>%
  filter(gamma >= 0.75) %>%
  distinct(title, .keep_all = T) %>%
  filter(topic %in% keep) %>%
  # Filter documents about the death of H.Geißler
  filter(!grepl("Geißler", title)) %>%
  # Filter outliner article (wrong topic assignment)
  filter(document != 9725) %>%
  filter(!grepl("Thermilindner", title, ignore.case = T))

@@

#### 2.2.3. Check the analysis for a set of example documents.

@@

#### 2.2.4. Calculate sentiment value by document

The sentiment score is calculated based on the weighted polarity values for a word, defined on an interval between -1 and 1. The score is then calculated from the sum of the words in a document (which can be assigned to a word from the dictionary) divided by the total number of words in that document.

@@

@@

  # combine with dataframe
  left_join(., df, 
            by = "document") %>%
  # calculate sentiment
  mutate(sentiment_d = sent_diff_d / text_length,
         sentiment = sent_diff / text_length) %>%

  # generate week
  mutate(week = week(date),
         month = as.character(month)) %>%
  mutate(week = paste(month,week, sep = "-"))
```

#### 2.2.5. Plot Sentiment Score

The following figure shows the results of the analysis for each topic on a monthly basis, aggregated on all newspaper. Some conclusions can be drawn from this illustration. First of all, it is clear that topics concerning the AfD (20, 30, 32, 37) are discussed in a negative way over the entire period, with an exepction for topic 30, dealing with Frauk Petry and the AfD. The topic that is discussed most negatively is that of the right-wing extremist tendencies within the AfD. Another striking result is that the sentiment score of topics topics that deal with the SPD alone (1, 22) is diminishing in the course of time. The topic, which contains the CDU in isolation (46), is rather zigzagging, with a high peak in November 2017 and a low peak in January 2018, but there is only one observation this month, which is an article about Peter Tauber's illness.

Concerning the issues that discuss possible coalitions, it is evident that there was a month in which the Jamaican coalition was positively discussed (topic 27): October 2017, when coalition talks were in full swing. With the failure of the negotiations, the sentiment value of the articles also decreases, while the number of articles dealing with this topic increases sharply in the short term (to 210 articles) and decreases significantly in the following months. It is striking that precisely at this time (December 2017), both the observations, as well as the sentiment value of the articles that report on the grand coalition increase (topic 4).

##### By Month & Topic
```{r fig.height=10, fig.width=12}
p <- sentDF.values %>%
  group_by(month, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            sentiment_d = mean(sentiment_d, na.rm=T),
            obs = n()) %>%
  ungroup()

p1 <- ggplot(p, 
       aes(month, sentiment, 
           group = topic_name,
           label = obs)) +
  facet_wrap(~topic_name, nrow = 3) +
  geom_col(fill = col[1], alpha = 0.7) +
 geom_line(color = col[2], size = 1) +
  geom_text() +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  labs(x="", y="",
       title = "Monthly Sentiment Score") +
  theme(axis.text.y = element_text(size=8),
        axis.text.x = element_text(angle = 90, size = 6))

##### By Site and Topic

```{r fig.height=5, fig.width=10}
p <- sentDF.values %>%
  group_by(site, topic_name, topic) %>%
  summarise(sentiment = mean(sentiment, na.rm=T),
            sentiment_d = mean(sentiment_d, na.rm=T),
            obs = n())

p1 <- ggplot(p, 
       aes(reorder(topic_name, topic), 
           sentiment, label = obs)) +
  geom_col(fill=col[2], alpha = 0.7) +
  geom_text(size = 2.5) +
  geom_hline(yintercept = 0, linetype = 2,
             color = "black") +
  coord_flip() +
  facet_wrap(~site, ncol = 7) +
  labs(x="", y="",
       title = "Sentiment Score") +
  theme(axis.text.y = element_text(size=8),
        axis.text.x = element_text(angle = 90))

##### Radar plot

@@

```{r fig.height=10, fig.width=10}
sentDF.values %>%
  group_by(site, topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T)) %>%
  spread(key=topic_name, value=sentiment) -> radar

radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0, legend.position = "right") +
  labs(title = "Sentiment score Jun 2017-March 2018") +
  guides(col = guide_legend(nrow = 1)) +
  theme(legend.position = "bottom")
```

```{r eval=FALSE, include=FALSE}
for (i in unique(sentDF.values$month)) {

  sentDF.values %>%
  filter(month == i) %>%
  group_by(site, topic_name) %>%
  summarise(sentiment = mean(sentiment, na.rm=T)) %>%
  spread(key=topic_name, value=sentiment) -> radar

  p <-radar %>%
    ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0, legend.position = "right") +
  labs(title = paste("Sentiment Score", i))

  ggsave(p, filename = paste0("../figs/radarchart_",i,".png"), 
         device = "png", dpi = 600)

@@

<!-- <img src="../figs/radarchart_2017-06.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2017-07.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2017-09.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2017-10.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2017-11.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2017-12.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2018-01.png", width = "49%"> -->
<!-- <img src="../figs/radarchart_2018-02.png", width = "49%"> -->

### 2018-03-12 paper/writing/doc_backup.tex
its getting better...

>>>>

\begin{enumerate}
	\item \textbf{Discovering Topics (Section \ref{ch_model})} To discover the latent topics in the corpus, the structural topic modeling (STM) developed by \citet{roberts_model_2016} is applied. The STM is an unsupervised machine learning approach that models topics as multinomial distributions of words and documents as multinomial distributions of topics, allowing to incorporate external variables that effect both, topical content and topical prevalence. I estimate a model, where the newswire service is included as a control for both the topical content and the topical prevalence. The result of the generative process of STM are the posterior distributions for topic prevalence and topical content, which can then be used to measure the similarity between private and public news providers in the further course of the paper: (1) $\beta$ is a $K$-by-$V$ matrix (where $K=$ number of topics and $V=$ vocabulary), where the entry $\beta_{kvc}$ can be interpreted as the probability of observing the $v$-th word in topic $k$ for the covariate level $c$. (2) $\theta$ is a $D$-by-$V$ matrix of the document-topic distributions, where the entry $\theta_{dk}$ can be interpreted as the proportion of words in document $d$ which arise from topic $k$, or rather as the probability that document $d$ deals about topic $k$.

	\item \textbf{Measuring Similarity of news content} Different approaches are used to examine similarities and/or differences of content between the news provider:
	\begin{enumerate}
		\item\label{item_1}\textbf{Differences in topic prevalence:} As I allow prevalence of topics to evolve over time (by month) and vary across business models, the posterior topic-probability $\theta_{dk}$ of document can be used to estimate the conditional expectation of topic prevalence for given document characteristics.

		\item\label{item_2} \textbf{Topic correlation} To get an idea of how topics are linked and framed differently across news wires, the correlation of the posterior probability of topics $\theta_{dk}$ is calculated.

		\item\label{item_3} \textbf{Differences in word-topic distributions} As each row of $\beta_{kvc}$ corresponds to the word-distribution of a respective topic for the covariate level $c$, it can be used to calculate the similarity of the word-topic distribution between the news provider using established similarity measures.

		\end{enumerate}

\end{enumerate}
